---
title: "K-Means Clustering Example"
author: "Renu Mary Daniel"
date: "01/04/2020"
output:
  html_document: default
  pdf_document: default
---

## Loading Data and Packages   

```{r load}
library(cluster.datasets)
data("all.mammals.milk.1956")
head(all.mammals.milk.1956)
```

## Checking data provenance   

```{r prov}
library(digest)
h1<-"f4ff686f92c89e326a6360ac920a06a014ef35c1"
paste('checked at',date())
df<-all.mammals.milk.1956
h2<-digest(as.character(df),algo="sha1")
stopifnot(identical(h1, h2))
```
Execution continues since both the hashes are equivalent.

## Preparing Data for Clustering

Producing reproducible work using set.seed()
```{r reprod,eval=T}
set.seed(123)
input<-all.mammals.milk.1956[,2:6]
head(input)
```

## Applying K-means clustering
```{r clust}
library(cluster)
clus<-kmeans(input,centers=3,nstart=20)
clus
```

Here, we have k-means clustering with 3 clusters and 20 initial random starts  

## Visualizing the optimal number of clusters
```{r visual1}
library(factoextra)
fviz_nbclust(input,kmeans,method="wss")
```

It is obvious from the plot that the within cluster sums of squares is optimal at value 4  

## Visualizing the clusters  

```{r visual2}
fviz_cluster(clus,data=input) #fviz_cluster helps in visulization of clusters 
```
  
## Saving the Workspace
```{r save,echo=T,eval=T,cache=F,message=F}
save(list = ls(all.names = TRUE), file = "SampleSpace.RData", envir = .GlobalEnv)
fname="SampleSpace.RData"
message(paste('saved',fname)) # message to running R console
print(paste('saved',fname)) # print to document
```